CEP Group Meeting

### 2023-07-25 output/presentations/cep_internal_230726/presentation.qmd
Finished presentation for CEP meeting.

```{r}
#| include: false
here::i_am("presentation.qmd")
```

@@

- URL manual: https://isglobal-cep.github.io/myphd/
- To install it: `remotes::install_github("isglobal-cep/myphd")`

@@

![`Correlation numerical variables.`](artwork/corr.png)

## Preliminary results

@@

- `lmtp` will be the focus of my research stay with ... at ...

>>>>

```{r}
#| include: false
here::i_am("presentation.qmd")

library(patchwork)
```

@@

- URL manual: https://isglobal-cep.github.io/myphd/
- To install it: `remotes::install_github("isglobal-cep/myphd")`.

@@

![Correlation numerical variables.](artwork/corr.png)

## Preliminary results: weights

```{r}
targets::tar_load(c("weights", 
                    "weighted_fits", 
                    "marginal"), 
                  store = paste0(
                    "~/mounts/rstudioserver/PROJECTES/HELIX_OMICS/",  
                    "DATA_PREVIOUS_MIGRATION/lorenzoF/", 
                    "data/data_paper3/_targets/_targetsRQ2/"
                  ))
```

```{r}
weights$balance$hs_bpa_c$love
```

## Preliminary results: weighted G-computation

- Marginal effects of exposure to non-persistent EDCs on Cortisone: comparison `Q3 - Q1`.

![Effect estimates for EDCs and Cortisone.](artwork/effects_cortisone.png){width=130%, fig-align="center"}

```{r}
gtsummary::tbl_summary(weighted_fits$fits$hs_bpa_c$dat |>
                         dplyr::rename(BPA = hs_bpa_c, 
                                       cortisone = Cortisone_E), 
                       include = c("BPA", "cortisone"), 
                       by = "cohort") |>
  gtsummary::add_overall() |>
  gtsummary::as_kable_extra(booktabs = TRUE) |>
  kableExtra::kable_styling(latex_options = "scale_down")
```

## Preliminary results: ADRF and AMEF

```{r}
marginal$marginal_effects$hs_bpa_c$adrf / 
  marginal$marginal_effects$hs_bpa_c$amef
```

@@

- Dealing with creatinine.

![Comparison of effect estimation.](artwork/comp_creatinineAdj.png)

- Developing a more appropriate pipeline to deal with censored exposures and metabolites.

- Dealing with more appropriate modeling strategies?

  - `lmtp` will be the focus of my research stay (*Mixtures done right*) under the supervision of Prof. Jessica G. Young and Prof. Ivan Diaz (who formalized causal identification of interventions that depend on the natural value of treatment).
